Preprocessing

### 2024-01-05 analysis/preprocessing.Rmd
Corrected logic coding error
Noticed T/F coding for d_articles$ppc_linked was inverted.

```{r}
d_articles <- d_articles %>%
  mutate(sample_id = factor(sample_id),
         article_id = factor(article_id),
         exclude = factor(exclusion_final),
         exclude_reason = factor(exclusion_reason_final),
         ppc_linked = as.logical(fct_recode(ppc_linked_final, T = "NO", F = "YES"))) %>%
  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
```

>>>>

```{r}
d_articles <- d_articles %>%
  mutate(sample_id = factor(sample_id),
         article_id = factor(article_id),
         exclude = factor(exclusion_final),
         exclude_reason = factor(exclusion_reason_final),
         ppc_linked = as.logical(fct_recode(ppc_linked_final, F = "NO", T = "YES"))) %>%
  select(sample_id, article_id, exclude, exclude_reason, ppc_linked)
```
